`r spec$datasetname`

### 2025-09-01 report/template.qmd
nobs -> revision_history

rev_data <- lapply(basename(list_files), function(f){
    res <- lapply(studied_methods, function(method) {
        read.ts(file.path(dirname(params$file), spec$dataset, method, f), list = TRUE)[series]
    })
    c(list("Série CVS-CJO" = lapply(all_data[[tools::file_path_sans_ext(f)]], window, 
                               start = min(sapply(spec_series, `[[`, "first_date")))),
      res)
})
names(rev_data) <- names(all_data)
rev_data <- rev(rev_data)
rev_data_ <- lapply(names(rev_data[[1]][[1]]), function(serie){
    res <- lapply(names(rev_data[[1]]), function(method){
        do.call(ts.union, lapply(rev_data, function(x){
            x[[method]][[serie]]
        }))
    })
    names(res) <- names(rev_data[[1]])
    res
})
names(rev_data_) <- names(rev_data[[1]][[1]])
rev_data <- rev_data_
rm(rev_data_)
```

```{r}
#| label: revision-history-contribution-sa
#| eval: !expr spec$plots$revision_history$enabled & spec$plots$revision_history$table$contribution_of_sa
rev_data_fixed <- lapply(series, function(serie) {
    spec_s <- spec$series[[serie]]
    y <- window(all_data[[n]][[serie]], start = spec$series[[serie]]$first_date)
    dates <- all_data[-n]
    if (!is.null (spec$plots$revision_history$table$nobs)) 
        dates <- tail(dates, spec$plots$revision_history$table$nobs - 1)
    vintages <- lapply(dates, function(vintage){
        window(y, end = end(vintage[[serie]]))
    })
    lapply(studied_methods, function(method) {
        method_name <- names(studied_methods)[which(studied_methods == method)]
        res <- c(lapply(vintages, function(x) {

@@

rev_tot <- lapply(series, function(serie) {
    rev_by_method <- lapply(names(studied_methods), function(method){
        data <- rev_data_fixed[[serie]][[method]]
        data_tot <- rev_data[[serie]][[method]]
        rev_tc <- (data[,1] - data)
        rev_tot <- (data_tot[,1] - data_tot)
        rev_tot <- rev_tot
        rev_sa <- rev_tot - rev_tc
        colnames(rev_tc) <- colnames(rev_sa) <- colnames(rev_tot) <- colnames(data_tot)
        list(
            Total = rev_tot, 
            `Due to revisions on SA` = rev_sa, 
            `Due to update of TC model` = rev_tc
        )
    })
    names(rev_by_method) <- names(studied_methods)
    rev_tot_by_method <- do.call(
        rbind,
        lapply(names(rev_by_method), function(method){
            rev_meth <- rev_to_table(rev_by_method[[method]], nobs = spec$plots$revision_history$table$nobs)
            cbind(Meth = method, rev_meth)
        })
    )
    rev_tot_by_method <- rev_tot_by_method[rev_tot_by_method[, "Last date"] != colnames(rev_tot_by_method)[4], -4]
    rev_tot_by_method[with(rev_tot_by_method, order(Meth,-xtfrm(`Last date`), Methods)), ]
})
```

>>>>

rev_data <- lapply(basename(list_files), function(f){
    res <- lapply(studied_methods, function(method) {
        read.ts(file.path(dirname(params$file), spec$dataset, method, f), list = TRUE)[series]
    })
    c(list("Série CVS-CJO" = lapply(all_data[[tools::file_path_sans_ext(f)]], window, 
                               start = min(sapply(spec_series, `[[`, "first_date")))),
      res)
})
names(rev_data) <- names(all_data)
if (!is.null (spec$plots$revision_history$nobs)) 
    rev_data <- tail(rev_data, spec$plots$revision_history$nobs)
rev_data <- rev(rev_data)
rev_data_ <- lapply(names(rev_data[[1]][[1]]), function(serie){
    res <- lapply(names(rev_data[[1]]), function(method){
        do.call(ts.union, lapply(rev_data, function(x){
            x[[method]][[serie]]
        }))
    })
    names(res) <- names(rev_data[[1]])
    res
})
names(rev_data_) <- names(rev_data[[1]][[1]])
rev_data <- rev_data_
rm(rev_data_)
```

```{r}
#| label: revision-history-contribution-sa
#| eval: !expr spec$plots$revision_history$enabled & spec$plots$revision_history$table$contribution_of_sa
rev_data_fixed <- lapply(series, function(serie) {
    spec_s <- spec$series[[serie]]
    y <- window(all_data[[n]][[serie]], start = spec$series[[serie]]$first_date)
    dates <- all_data[-n]
    if (!is.null (spec$plots$revision_history$nobs)) 
        dates <- tail(dates, spec$plots$revision_history$nobs - 1)
    vintages <- lapply(dates, function(vintage){
        window(y, end = end(vintage[[serie]]))
    })
    lapply(studied_methods, function(method) {
        method_name <- names(studied_methods)[which(studied_methods == method)]
        res <- c(lapply(vintages, function(x) {

@@

rev_tot <- lapply(series, function(serie) {
    rev_by_method <- lapply(names(studied_methods), function(method){
        data <- rev_data_fixed[[serie]][[method]]
        data_tot <- rev_data[[serie]][[method]]
        rev_tc <- (data[,1] - data)
        rev_tot <- (data_tot[,1] - data_tot)
        rev_tot <- rev_tot
        rev_sa <- rev_tot - rev_tc
        colnames(rev_tc) <- colnames(rev_sa) <- colnames(rev_tot) <- colnames(data_tot)
        list(
            Total = rev_tot, 
            `Due to revisions on SA` = rev_sa, 
            `Due to update of TC model` = rev_tc
        )
    })
    names(rev_by_method) <- names(studied_methods)
    rev_tot_by_method <- do.call(
        rbind,
        lapply(names(rev_by_method), function(method){
            rev_meth <- rev_to_table(rev_by_method[[method]], nobs = spec$plots$revision_history$nobs)
            cbind(Meth = method, rev_meth)
        })
    )
    rev_tot_by_method <- rev_tot_by_method[rev_tot_by_method[, "Last date"] != colnames(rev_tot_by_method)[4], -4]
    rev_tot_by_method[with(rev_tot_by_method, order(Meth,-xtfrm(`Last date`), Methods)), ]
})
```
